Fixing Vulnerabilities Potentially Hinders Maintainability

### 2020-08-21 paper/emse20.tex
images update

\begin{table}[h]
\scriptsize
	\caption{Guidelines to produce maintainable code}
\begin{tabular}{L{1.66cm}L{3.3cm}L{2.7cm}}

@@

\begin{figure}[h]
 	\centering 	
	\includegraphics[width=0.6\linewidth]{figures/commit.pdf}
 	\caption{Maintainability difference for security commits}
	\label{fig:commit}
\end{figure}

@@

 \begin{figure}[htp]
     \begin{adjustwidth}{-1cm}{-1cm}  
  	\centering
  	\includegraphics[width=0.51\textwidth]{figures/main_per_guideline.pdf}
    \end{adjustwidth}

@@

 \begin{figure}[htp]
  	\centering 	
 	\includegraphics[width=0.4\textwidth]{figures/main_per_severity.pdf}
  	\caption{Maintainability difference by vulnerability severity.}
 	\label{fig:severity}
 \end{figure}

@@

\begin{figure}[htp]
  \centering
  \includegraphics[width=0.4\textwidth]{figures/main_per_language.pdf}
  \caption{Maintainability difference by programming language.}
  \label{fig:lang_main}    
\end{figure}

@@

\begin{figure}[htp]
 	\centering 	
	\includegraphics[width=0.5\textwidth]{figures/main_comparison.pdf}
 	\caption{Maintainability difference for security and baseline patches.}
	\label{fig:secvsreg}
\end{figure}

>>>>

\begin{table}[H]
\centering
\scriptsize
	\caption{Guidelines to produce maintainable code}
\begin{tabular}{L{1.66cm}L{3.3cm}L{2.7cm}}

@@

\begin{figure}[h]
 	\centering 	
	\includegraphics[width=0.9\linewidth]{figures/commit.pdf}
 	\caption{Maintainability difference for security commits}
	\label{fig:commit}
\end{figure}

@@

 \begin{figure}[htp]
     \begin{adjustwidth}{-1cm}{-1cm}  
  	\centering
  	\includegraphics[width=0.8\textwidth]{figures/main_per_guideline.pdf}
    \end{adjustwidth}

@@

 \begin{figure}[htp]
  	\centering 	
 	\includegraphics[width=0.6\textwidth]{figures/main_per_severity.pdf}
  	\caption{Maintainability difference by vulnerability severity.}
 	\label{fig:severity}
 \end{figure}

@@

\begin{figure}[htp]
  \centering
  \includegraphics[width=0.6\textwidth]{figures/main_per_language.pdf}
  \caption{Maintainability difference by programming language.}
  \label{fig:lang_main}    
\end{figure}

@@

\begin{figure}[htp]
 	\centering 	
	\includegraphics[width=0.7\textwidth]{figures/main_comparison.pdf}
 	\caption{Maintainability difference for security and baseline patches.}
	\label{fig:secvsreg}
\end{figure}
